%!TEX root = ./miller-cooks.tex
%!TEX encoding = UTF-8 Unicode
%!TEX spellcheck = en-US

\pagestyle{empty}
\MyTitlePage{} % this does a \clearpage

\begin{CopyrightPage}
    {
    First Beta Edition (file created \today ) \par
    \CopyrightInfo{}\par

    No part of this publication may be reproduced, distributed, or transmitted in any form or by any means,
    including photocopying, recording, or other electronic or mechanical methods, without the prior written
    permission of the publisher, except in the case of brief quotations embodied in critical reviews and
    certain other noncommercial uses permitted by copyright law. For permission requests, write to the
    publisher at the address below. \par
    \vspace{5pt}
    ISBN No: {\textsb{978-3-00-000000-0}}\par
    Library of Congress Control Number: {\textsb{00000000000}} \par
    \vspace{5pt}
    Publisher: \par
    Example Publisher\par
    111 Address St.\par
    City, State, 12345\par
    www.theirwebsite.com

    \vspace{5pt}
    \hrule
    \vspace{5pt}
    The formatting/layout of this book was produced using MiK\TeX\space (with the Lua\TeX\space compiler),
    which is a software front-end for the \TeX\space / \LaTeX\space typesetting and document preparation
    system.  See also the \textsb{makecookbook} bundle at:

    \quad https://ctan.org/pkg/makecookbook

    \vspace{5pt}
    The fonts used in this book are:\par
    \vspace{6pt}
    \ColophonFonts{}
    \vspace{5pt}
    Front cover image by [Artist].\par
    Book design by Terrence P. Murphy and Rosalie A. D'Amico.\par
    Printed by [printer name here], in the United States of America. \par
    }
\end{CopyrightPage}  % ends with a \clearpage

\MyDedication{}
\newpage

\DedicationVerso{} % Optional content for the usually empty verso page after the dedication (and before TOC)
\newpage

% The \pagestyle{main} call seems to be "in time" to apply to the \tableofcontents
% (and I even tested making the TOC two pages and the first page was still correct)

\tableofcontents
\pagestyle{main}

\chapter{Preface}
\ChapterIntro{
    This is the start of Caitlyn's cookbook. Sure, there are a few non-\emph{minor} things on this list
    (particularly all the Margarita recipes) but most are things that we make often. Eventually
    we'll get around to making this look like a real cookbook. Well, at least we'll make it so
    it's nicely formatted so Caitlyn can take it with her wherever she might go.

    This ``cookbook'' got its start because Caitlyn loves to cook but wanted to make sure she
    had ``all the recipes'' in hand in case she needed them. Many, but not most, of these came
    from somewhere else but have been heavily modified to meet the weird dietary needs to the
    Miller Family. They're not too weird that a ``normal'' person would find these recipes
    strange or gross. In fact, quite the opposite.

    Enjoy.
}

