\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{mathabx} % Required for hash sign
\usepackage{xfrac} % Nice fractions

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\pagestyle{fancy}

\rhead{Desserts and sweets}
\lhead{\textbf{M \& M Cookies}}
\chead{}
\title{M \& M  Cookies}

\begin{document}

This is a simple variation on a classic Chocolate Chip Cookie recipe. I ended up making it one
time when I only had a bag of mini M \& M's, didn't have the bag of chocolate chips, and was being
asked (demanded of, actually) for some cookies.

\textbf{Ingredients}

\begin{multicols}{2}
      \begin{itemize}
            \item 2\sfrac{1}{2} cups all purpose flour
            \item 1 teapoon baking soda
            \item \sfrac{1}{2} teapoon salt

            \item 1 cup butter, softened slightly
            \item \sfrac{3}{4} cup granulated sugar
            \item \sfrac{3}{4} cup packed light brown sugar

            \item 2 teaspoons vanilla
            \item 2 large eggs
            \item 12 ounce bag mini M \& M's (2 cups)
      \end{itemize}
\end{multicols}

\textbf{Directions}

\begin{enumerate}
      \item Preheat oven to 375 degrees.
      \item Whisk the flour, baking soda, and salt in a small bowl.
      \item Cream the butter and sugars together until light and fluffy. You want to make sure you get
            enough air into the mixture and cut all that butter nicely.
      \item Add the vanilla and the eggs, one egg at a time. Beat the wet ingredients until quite smooth.
      \item Slowly add, about a cup at a time, the dry ingredients to the mixer and mix well.
      \item Once the dry and wet ingredients and combined beat on low-medium (3) until
            everything is smooth.
      \item Fold in the M \& M's. Make sure they're well incorporated but do not over beat.
      \item Using a medium $\varhash 30$ scoop spoon the dough onto parchment-lined cookie sheets.
      \item Bake for 8 to 10 minutes or until done or until just starting to turn golden brown.
\end{enumerate}

\medskip

\textbf{Note}: If you make these with a $\varhash 20$ scoop the recipe yields about 5 dozen cookies.

% I suppose pictures could go here

\end{document}
