\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{xfrac} % Nice fractions
\usepackage{amsmath}

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\pagestyle{fancy}

\rhead{Desserts and sweets}
\lhead{\textbf{Peanut Butter Thumbprints}}
\chead{}
\title{Peanut Butter Thumbprints}

\begin{document}


\textbf{Ingredients}

\begin{itemize}
      \item 48 Hershey Kisses, unwrapped
      \item \sfrac{1}{2} cup shortening
      \item \sfrac{3}{4} cup chunky peanut butter
      \item \sfrac{1}{3} cup granulated sugar
      \item \sfrac{1}{3} packed light brown sugar
      \item 1 egg
      \item 2 tablespoons milk
      \item 2 teaspoons vanilla
      \item 1\sfrac{1}{2} cups all purpose flour
      \item 1 teapoon baking soda
      \item \sfrac{1}{2} teapoon salt
      \item \sfrac{1}{2} cup granulated sugar for rolling
\end{itemize}

\textbf{Directions}

\begin{enumerate}
      \item Preheat oven to 375 degrees.
      \item Beat hard the shortening and peanut butter with the granulated and brown sugars
            until light and fluffy, about 3 minutes. Make sure to scrape the sides of the
            mixer several times.
      \item On medium speed beat in the egg, milk, and vanilla.
      \item Whisk the flour, baking soda, and salt in a medium bowl. Gradually mix the dry ingredients
            into the peanut butter mixture.
      \item Using the medium scoop form balls of dough. Roll each each ball in a bowl with the
            additional granulated sugar.
      \item Place the balls on a parchment lined cookie sheet. You should put about 12 cookies
            on each sheet.
      \item Bake 8 to 10 minutes or until lightly browned. Immediately press a kiss into the center
            of each cookie (they're going to crack around the edges, this is ok).
      \item Slide the cookies and parchment to a wire cooling rack and cool completely.
\end{enumerate}


% I suppose pictures could go here

\end{document}
