\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{mathabx} % Required for hash sign
\usepackage{xfrac} % Nice fractions

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\pagestyle{fancy}

\rhead{Desserts and sweets}
\lhead{\textbf{Peanutty Peanut Butter}}
\chead{}
\title{Peanutty Peanut Butter}

\begin{document}

It's always fun to smash up ingredients. It really is. In this case we get to smash up some peanuts to
make a really chunky version of our own peanut butter. Don't worry, we're going to add even more
chunky peanut butter while we're going. These peanut butter cookies end up with a nice smooth texture
because there's so much butter. If you don't like ``sandy'' peanut butter cookies then these are for you.

These cookies, if done right, end up thick and chewy with just the right amount of slightly sweet-salty
peanutty flavor. Oh, the honey, that's because honey is hygroscopic, which means it attracts water
and helps keep the cookies moist. After you unwrap the butter keep the wrappers as they'll have just
enough butter left to coat the bottom of the glass.

\textbf{Ingredients}

\begin{multicols}{2}

      \begin{itemize}
            \item 2\sfrac{1}{2} cups all purpose flour
            \item \sfrac{1}{2} teapoon baking powder
            \item \sfrac{1}{2} teapoon baking soda
            \item \sfrac{1}{4} teapoon salt

            \item \sfrac{3}{4} cup butter
            \item \sfrac{1}{3} cup granulated sugar
            \item 1 cup packed light brown sugar
            \item \sfrac{3}{4} cup chunky peanut butter
            \item 1 tablespoon honey
            \item 1 teaspoon vanilla
            \item 2 large eggs

            \item 1\sfrac{1}{2} cups salted snacking peanuts
            \item granulated sugar for sprinkling
      \end{itemize}
\end{multicols}

\textbf{Directions}

\begin{enumerate}
      \item Preheat oven to 375 degrees.
      \item Mix the flour, baking powder, baking soda, and salt in a small bowl.
      \item Cream the butter and sugars together until light and fluffy. You want to make sure you get
            enough air into the mixture and cut all that butter nicely.
      \item Add the peanut butter, honey, eggs, and vanilla and beat until light and fluffy again.
      \item Put the peanuts in a zipper lock bag and roll them until they are like a coarse sand. You
            don't want mush, but you don't want whole peanuts either.
      \item Using a medium $\varhash 30$ scoop spoon the batter onto parchment-lined cookie sheets. Using
            the bottom of a buttered and sugared glass press the cookies until they are between \sfrac{1}{2}
            and \sfrac{3}{4} inches thick. Make sure you're consistent. Sprinkle each cookie with a little
            more granulated sugar.
      \item Bake for 9 to 10 minutes or until done, but do not overbake them. Let them sit on the baking
            sheet for a few additional minutes before removing to a wire rack to completely cool.
\end{enumerate}


% I suppose pictures could go here

\end{document}
