\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{mathabx} % Required for hash sign
\usepackage{xfrac} % Nice fractions

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\pagestyle{fancy}

\rhead{Desserts and sweets}
\lhead{\textbf{Sugar Cookies}}
\chead{}
\title{Sugar Cookies}

\begin{document}

Yet another Cooks Illustrated Baking-inspired recipe. But, as with most of the recipes in that
book, Dad had to mess with it\dots

These are not decoration sugar cookies. That's a completely different recipe. These are soft
and chewy.

\textbf{Ingredients}

\begin{multicols}{2}
    \begin{itemize}
        \item 2\sfrac{1}{4} cups all purpose flour
        \item \sfrac{1}{2} teapoon baking powder
        \item \sfrac{1}{4} teapoon salt

        \item 2 sticks butter, softened slightly, but still cool
        \item 1 cup granulated sugar, plus \sfrac{1}{2} for rolling
        \item 1 tablespoon light brown sugar

        \item 1 large egg
        \item 2 teaspoons vanilla
    \end{itemize}
\end{multicols}

\textbf{Directions}

\begin{enumerate}
    \item Preheat oven to 375 degrees.
    \item Whisk the flour, baking powder, and salt in a small bowl.
    \item Cream the butter and sugars together until light and fluffy. You want to make sure you get
          enough air into the mixture and cut all that butter nicely.
    \item Add the vanilla and the eggs, one egg at a time. Beat the wet ingredients until quite smooth.
    \item Add the dry ingredients to the mixer and mix well.
    \item Using a medium $\varhash 30$ scoop spoon the dough onto parchment-lined cookie sheets.
    \item Roll each dough ball in the granulated sugar until well coated.
    \item Using the bottom of a flat-bottomed glass, coated in butter and dipped in sugar,
          flatten the cookied to \sfrac{3}{4} inch thick
    \item Bake for 15 to 18 minutes rotating the pans top to bottom and back to front halfway
          through baking. Let cool 3 minutes on the baking sheet before moving to a wire rack.
\end{enumerate}

\medskip

\textbf{Note}: I just happened to have picked a bunch of fresh lemons one morning when I
made these. So, I made a quick lemon glaze using about \sfrac{1}{2} cup powdered sugar and
just enough lemon juice to make a spreadable glaze. After the cookies are completely cooled,
pour the glaze over them.

Another alternative, since these are really light cookies is to grate 2 to 3 tablespoons of
lemon zest into the wet ingredients to create a simple lemon sugar cookie. If you do this you
might want to cut the vanilla in half to 1 teapoon, increase the flour \sfrac{1}{4} cup and
add 2 teapoons of lemon juice.


\end{document}
