\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{mathabx} % Required for hash sign
\usepackage{xfrac} % Nice fractions
\usepackage{hyperref}

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=cyan,
    pdftitle={The Miller Family Cooks Stuff}
    }

\urlstyle{same}

\pagestyle{fancy}

\lhead{\textbf{The Miller Family \textit{Cooks Stuff}}}
\chead{}
\title{The Miller Family Cooks Stuff}

\begin{document}

This is the start of Caitlyn's cookbook. Sure, there are a few non-minor things on this list (particularly all the Margarita recipes) but most are things that we make often. Eventually
we'll get around to making this look like a real cookbook. Well, at least we'll make it so
it's nicely formatted so Caitlyn can take it with her wherever she might go.

This "cookbook" got it's start because Caitlyn loves to cook but wanted to make sure she
had "all the recipes" in hand in case she needed them. Many, but not most, of these came
from somewhere else but have been heavily modified to meet the weird dietary needs to the
Miller Family. They're not too weird that a "normal" person would find these recipes
strange or gross. In fact, quite the opposite.

Enjoy.

\textbf{Breads}
\begin{itemize}
    \item \href{french-bread.pdf}{French Bread}
    \item \href{wheat-bread.pdf}{Wheat Bread}
\end{itemize}

\medskip

\textbf{Main Courses}
\begin{itemize}
    \item \href{chicken-teriyaki.pdf}{Chicken Teriyaki}
    \item \href{dads-meatballs.pdf}{Dad's Meatballs}
    \item \href{fried-chicken.pdf}{Fried Chicken}
    \item \href{lettuce-wraps.pdf}{Lettuce Wraps}
    \item \href{moms-meatballs.pdf}{Mom's Meatballs}
    \item \href{tuna-pasta-salad.pdf}{Tuna Pasta Salad}
\end{itemize}

\medskip

\textbf{Desserts and Sweets}
\begin{itemize}
    \item \href{chocolate-chip.pdf}{Chocolate Chip Cookies}
    \item \href{lemon-bars.pdf}{Lemon Bars}
    \item \href{m-and-m-cookies.pdf}{M\&M Cookies}
    \item \href{molasses-cookies.pdf}{Molasses Cookies}
    \item \href{oatmeal-cookies.pdf}{Oatmeal Cookies}
    \item \href{peanut-butter.pdf}{Peanutty Peanut Butter}
    \item \href{peanut-butter-thumbprints.pdf}{Peanut Butter Thumbprints}
    \item \href{snickerdoodles.pdf}{Snickerdoodles}
    \item \href{sugar-cookies.pdf}{Sugar Cookies}
    \item \href{todd-bardal.pdf}{Todd Bardal Cookies}
    \item \href{white-choco-macadamia.pdf}{White Chocolate Macadamia}
\end{itemize}

\medskip

\textbf{Libations}
\begin{itemize}
    \item \href{hot-toddy.pdf}{Dad's Sore Throat Remedy}
    \item \href{grapefruit-rita.pdf}{Grapefruit Rita}
    \item \href{habanero-syrup.pdf}{Habanero Syrup}
    \item \href{mango-rita.pdf}{Mangorita}
    \item \href{mike-a-rita.pdf}{Mike-a-Rita}
\end{itemize}

\medskip

\textbf{Other stuff}
\begin{itemize}
    \item \href{salsa.pdf}{Roasted tomato salsa}
\end{itemize}

\textbf{Remaining recipes}
\begin{itemize}
    \item Mom:
          \begin{itemize}
              \item meat sauce
              \item  chk parmesan
              \item  nummy chk and pasta
              \item  tacos
              \item  chili
              \item  peanut butter/chocolate chip cookies
              \item  biscotti
              \item  kim's sugar cookies
              \item  frozen strawberry squares
          \end{itemize}

    \item Dad:
          \begin{itemize}
              \item  tacos
              \item  super bowl chicken nuggets
              \item  taquitos
              \item  blackened chicken
              \item  grilled chk
              \item  grilled potatoes
              \item  sugar cookies
              \item  chicken / turkey soup
              \item  vegetable soup
              \item  award-winning (adult) brownies
              \item  french bread
              \item  chili
              \item  deviled eggs
              \item  lasagna
              \item  chicken picatta
              \item  chicken marsala
              \item  grilled lemon chicken
              \item  potato salad
              \item  lemon cheese cake
          \end{itemize}

    \item Caitlyn: chicken fingers
          \begin{itemize}
              \item chicken fingers
          \end{itemize}

    \item PopPop:
          \begin{itemize}
              \item black bean dip
          \end{itemize}
\end{itemize}

\end{document}
