\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{mathabx} % Required for hash sign
\usepackage{xfrac} % Nice fractions

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\pagestyle{fancy}

\rhead{Desserts and sweets}
\lhead{\textbf{Todd Bardal Cookies}}
\chead{}
\title{Todd Bardal Cookies}

\begin{document}

Tihs recipe came from Nana's ``black book'' of recipes. We don't know where she got it, probably
from the NY Times. We've been making these \textit{forever} now and they're always a hit.

\textbf{Ingredients}

\begin{multicols}{2}
    \begin{itemize}
        \item 1\sfrac{3}{4} cups all purpose flour
        \item \sfrac{1}{2} teapoon baking soda
        \item \sfrac{1}{2} teapoon salt

        \item \sfrac{1}{2} cup butter, softened slightly
        \item \sfrac{1}{2} cup granulated sugar
        \item \sfrac{1}{2} cup packed light brown sugar

        \item 1 teaspoon vanilla
        \item 1 large egg
        \item \sfrac{1}{4} cup peanut butter
        \item 1 cup chocolate chips (\sfrac{1}{2} package)
    \end{itemize}
\end{multicols}

\textbf{Directions}

\begin{enumerate}
    \item Preheat oven to 375 degrees.
    \item Whisk the flour, baking soda, and salt in a small bowl.
    \item Cream the butter and sugars together until light and fluffy. You want to make sure you get
          enough air into the mixture and cut all that butter nicely.
    \item Add the vanilla and the eggs, one egg at a time. Beat the wet ingredients until quite smooth.
    \item Slowly add, about a cup at a time, the dry ingredients to the mixer and mix well.
    \item Fold in the chocolate chips and, if using, the walnuts. Make sure they're well
          incorporated but do not over beat.
    \item Using a medium $\varhash 30$ scoop spoon the dough onto parchment-lined cookie sheets.
    \item Bake for 10 to 12 minutes or until done or until just starting to turn golden brown.
\end{enumerate}

\medskip

% I suppose pictures could go here

\end{document}
