\documentclass{article}
\usepackage{lmodern} % Fix the font size warnings
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{mathabx} % Required for hash sign
\usepackage{xfrac} % Nice fractions

\usepackage{multicol}

% Margins
\topmargin=-0.5in
\evensidemargin=0in
\oddsidemargin=-0.5in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 

% paragraphs
\usepackage{parskip}

\pagestyle{fancy}

\rhead{Desserts and sweets}
\lhead{\textbf{White Chocolate Macadamia Cookies}}
\chead{}
\title{White Chocolate Macadamia Cookies}

\begin{document}

This recipe makes a bunch of cookies. How many? Well, about 6 dozen. Doesn't seem possible does it? Well,
if you follow the directions and use a $\varhash 20$ scoop you'll end up with that many tasty bite-sized
cookies. You can also use a $\varhash 30$ scoop to get slightly larger cookies. Buyer beware though because
these are really rich.

\textbf{Ingredients}

\begin{multicols}{2}

      \begin{itemize}
            \item 3 cups all purpose flour
            \item \sfrac{1}{2} teapoon baking soda
            \item 1 teapoon salt
            \item 1 cup butter, softened slightly
            \item 1\sfrac{1}{2} cups granulated sugar
            \item \sfrac{1}{2} cup packed light brown sugar
            \item 2 large eggs
            \item 1\sfrac{1}{2} teaspoon vanilla
            \item 12 ounce bag white chocolate chips (2 cups)
            \item 1\sfrac{1}{2} cups coarsely chopped macadamia nuts
      \end{itemize}
\end{multicols}

\textbf{Directions}

\begin{enumerate}
      \item Preheat oven to 350 degrees.
      \item Whisk the flour, baking soda, and salt in a small bowl.
      \item Cream the butter and sugars together until light and fluffy. You want to make sure you get
            enough air into the mixture and cut all that butter nicely.
      \item Add the vanilla and the eggs, one egg at a time. Beat the wet ingredients until quite smooth.
      \item Slowly add, about a cup at a time, the dry ingredients to the mixer and mix well.
      \item Once the dry and wet ingredients and combined beat on low-medium (3) until 
            everything is smooth.
      \item Fold in the white chocolate chips and the macadamia nuts. Make sure they're well
            incorporated but do not over beat.
      \item Using a small $\varhash 20$ scoop spoon the batter onto parchment-lined cookie sheets.
      \item Bake for 10 to 12 minutes or until done or until just starting to turn golden brown.
\end{enumerate}

\medskip

\textbf{Note}: Do not overbake these as they'll get quite dry and crunchy quickly. I tend to pull
them a minute or so early (at 11 minutes) and let them finish on the baking sheet out of the oven.
This leaves the cookies nice and soft in the middle with just enough crunch around the edges.

% I suppose pictures could go here

\end{document}
